%%%%%%%%%%%%%%%%%%%%%
% Friggeri Resume/CV
% XeLaTeX Template
% Version 1.0 (5/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Adrien Friggeri (adrien@friggeri.net)
% https://github.com/afriggeri/CV
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX and the bibliography, if used,
% needs to be compiled with biber rather than bibtex.
%
%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{friggeri-cv} % Add 'print' as an option into the square bracket to remove colors from this template for printing

\addbibresource{bibliography.bib} % Specify the bibliography file to include publications

\begin{document}

\header{David Lochridge}{}{Software Developer} % Your name and current job title/field

%----------------------------------------------------------------------------------------
%	SIDEBAR SECTION
%----------------------------------------------------------------------------------------

\begin{aside} % In the aside, each new line forces a line break
\section{Contact}
9912 Pitt Pl NE
Albuquerque, NM 87111
~
(505) 803 3839
~
\href{mailto:locd011@cs.unm.edu}{locd011@cs.unm.edu}
\section{Programming}
\subsection{Expert}
Java
Javascript
\subsection{Intermediate}
C, C++
C\# (Incl. .NET)
Haskell
HTML
Python
Ruby
VB (Incl. .NET)
\subsection{Beginner}
ASP.NET
Clojure
LaTeX
\section{Certifications}
Security+ (2015)
ASTQB Testing (2006)
\end{aside}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Education}

\begin{entrylist}
%------------------------------------------------
\entry
{2007--2014}
{Bachelors {\normalfont of Science}}
{The University of New Mexico, Albuquerque}
{Major in Computer Science, Minor in Russian Studies.}
%------------------------------------------------
\end{entrylist}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{Experience}

\begin{entrylist}
%------------------------------------------------
\entry
{Aug 2015--Now}
{Sandia National Laboratories}
{Albuquerque, New Mexico}
{\emph{Software System Engineer}} \\
Worked with a small team writing and maintaining custom software build and build support tools, and corporate applications such as GitHub, Artifactory, and Jenkins.\\
Detailed highlights:
\begin{itemize}
\item Wrote custom tool for detecting potentially sensitive code 
\item Wrote code for creating portable development and build environments
\item Adjusted and fixed custom build tool used in legacy project
\end{itemize}

\entry
{May 2014--Aug 2015}
{SAIC, Inc}
{Albuquerque, New Mexico}
{\emph{Software Developer} \\
Worked on a small team of developers maintaining over 50 applications, primarily written in Ruby on Rails, for Sandia National Laboratories.\\
Detailed highlights:
\begin{itemize}
\item Primary developer and contact for VB.NET and C++ projects.
\item Wrote a web application for coordinating group across ASC LDAP and AD
\item Wrote front and backend code for several visualizations in D3.
\item Wrote code for SlyCat, an open source project for ensemble analysis.
\begin{itemize}
		\item \href{https://github.com/sandialabs/slycat}{https://github.com/sandialabs/slycat}
\end{itemize}
\end{itemize}
}
%------------------------------------------------
\entry
{2013--May 2014}
{CAaNES, LLC}
{Albuquerque, New Mexico}
{\emph{Software Developer} \\
Wrote code for a web application that classified, visualized, and managed\\ security vulnerabilities, using Spring Framework and Maven in Java:
\begin{center}
	\href{https://risksense.com}{https://risksense.com}
\end{center}
Detailed highlights:
\begin{itemize}
\item Maintained data import portion of application.
\begin{itemize}
	\item Parsers for a variety of vulnerability and network scanners
\end{itemize}
\item Wrote web service for running and automatically importing scanner data.
\item Helped administer server hosted on Amazon Web Services.
\end{itemize}}
%------------------------------------------------
\entry
{2009--2013}
{Baker Hughes, Inc}
{Albuquerque, New Mexico}
{\emph{Software Tester} \\
Wrote and ran manual and automated tests for a geological modeling suite:
\begin{center}
	\href{http://jewelsuite.com}{http://jewelsuite.com (Redirects to bakerhughes.com)}
\end{center}
Detailed highlights:
\begin{itemize}
\item Designed and wrote automated tests in TestComplete using javascript.
\item Created and maintained virtual environments for compatibility testing
\end{itemize}
}
%------------------------------------------------
\end{entrylist}

%----------------------------------------------------------------------------------------
%	COMMUNICATION SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{Communication skills}

\begin{entrylist}
%------------------------------------------------
\entry
{2014}
{Senior Design Project}
{University of New Mexico}
{Project proposal and final project for CS460, Software Engineering.}
%------------------------------------------------
\entry
{2010--2013}
{Report}
{Baker Hughes, Inc}
{Created and presented annual report on performance and automated testing.}
%------------------------------------------------
 \end{entrylist}

%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------

\section{References}

Available on request.
\end{document}
