%%%%%%%%%%%%%%%%%%%%%
% Friggeri Resume/CV
% XeLaTeX Template
% Version 1.0 (5/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Adrien Friggeri (adrien@friggeri.net)
% https://github.com/afriggeri/CV
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX and the bibliography, if used,
% needs to be compiled with biber rather than bibtex.
%
%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{friggeri-cv} % Add 'print' as an option into the square bracket to remove colors from this template for printing

\addbibresource{bibliography.bib} % Specify the bibliography file to include publications

\begin{document}

\header{David Lochridge}{}{Software Developer} % Your name and current job title/field

%----------------------------------------------------------------------------------------
%	SIDEBAR SECTION
%----------------------------------------------------------------------------------------

\begin{aside} % In the aside, each new line forces a line break
\section{Contact}
9912 Pitt Pl NE
Albuquerque, NM 87111
~
(505) 803 3839
~
\href{mailto:locd011@gmail.com}{locd011@cs.unm.edu}
\section{Languages}
\subsection{Native}
English
\subsection{Functional}
Russian
\subsection{Elementary}
French
German
Spanish
\section{Programming}
\subsection{Expert}
Java
Javascript
\subsection{Intermediate}
C, C++
C\# (Incl. .NET)
Haskell
HTML
Python
Ruby
VB (Incl. .NET)
\subsection{Beginner}
ASP.NET
LaTeX
\end{aside}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Education}

\begin{entrylist}
%------------------------------------------------
\entry
{2007--2014}
{Bachelors {\normalfont of Science}}
{The University of New Mexico, Albuquerque}
{Major in Computer Science, Minor in Russian Studies.}
%------------------------------------------------
\end{entrylist}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{Experience}

\begin{entrylist}
%------------------------------------------------
\entry
{2014--Current}
{SAIC, Inc}
{Albuquerque, New Mexico}
{\emph{Software Developer} \\
Worked on a small team of developers maintaining 50 applications, primarily written in Ruby on Rails, for Sandia National Laboratories.\\
DOE Q Clearance pending. \\
Detailed highlights:
\begin{itemize}
\item Primary developer and contact for VB.NET and C++ projects.
\item Wrote front and backend code for several visualizations in D3.
\item Wrote code for SlyCat, an open source project for scientific data analysis.
\begin{itemize}
		\item \href{https://github.com/sandialabs/slycat}{https://github.com/sandialabs/slycat}
\end{itemize}
\end{itemize}
}
%------------------------------------------------
\entry
{2013--2014}
{CAaNES, LLC}
{Albuquerque, New Mexico}
{\emph{Software Developer} \\
Wrote code for a web application that classified, visualized, and managed\\ security vulnerabilities, using Spring Framework in Java:
\begin{center}
	\href{https://risksense.com}{https://risksense.com}
\end{center}
Detailed highlights:
\begin{itemize}
\item Maintained data import portion of application.
\begin{itemize}
	\item Parsers for a variety of vulnerability and network scanners including: Nessus, Nexpose, and Nmap
\end{itemize}
\item Wrote web service for running and automatically importing scanner data.
\item Helped manage and administer server hosted on Amazon Web Services.
\end{itemize}}
%------------------------------------------------
\entry
{2009--2013}
{Baker Hughes, Inc}
{Albuquerque, New Mexico}
{\emph{Software Tester} \\
Wrote and ran manual and automated tests for a geological modeling suite:
\begin{center}
	\href{http://jewelsuite.com}{http://jewelsuite.com (Redirects to bakerhughes.com)}
\end{center}
Detailed highlights:
\begin{itemize}
\item Designed and wrote automated tests in TestComplete using javascript.
\item Pioneered adding unit tests written in C\#.
\begin{itemize}
	\item Co-managed a team of offshore developers to expand tests.
\end{itemize}
\end{itemize}
}
%------------------------------------------------
\end{entrylist}

%----------------------------------------------------------------------------------------
%	COMMUNICATION SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{Communication skills}

\begin{entrylist}
%------------------------------------------------
\entry
{2014}
{Senior Design Project}
{University of New Mexico}
{Presented project proposal and final project for CS460--Software Engineering.}
%------------------------------------------------
\entry
{2010--2013}
{Report}
{Baker Hughes, Inc}
{Created and presented annual report on performance and automated testing.}
%------------------------------------------------
 \end{entrylist}

%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------

\section{References}

Available on request.
\end{document}
