\documentclass[11pt]{report}

\begin{document}

\begin{center}
	\Large\textbf{Final Self Evaluation CS 460}\\
	\Large{David Lochridge}
\end{center}

\begin{itemize}
\item[Work Components:]
	Blog: Should be better\\
	Team Contributions: Good


\item[Process Components:]
	Professionalism:	Good\\
	Quality:	Good\\
	Impact:	Good
\end{itemize}


As before, I had difficulties with using my blog, and did not enact the plan proposed in the midsemester evaluation. This needed to improve, and is still a problem.

Conversely, though, I contributed considerably more to the project than my fair share, and feel that that impact and those contributions outweigh the blog performance somewhat. As noted in the midsemester evaluation response, I feel that I improved the quality of class commentary and participation as well, which was a noted problem area before.

Contributions and Achievements:
\begin{itemize}
\item[-] Spoke in every class period possible (Nearly every one) and improved quality of comments somewhat
\item[-] Database design documents (Visible in the team turnin)
\item[-] Neither missed, nor was late to any client meetings.
\item[-] 117 out of the total 315 commits (37\%) as viewable in the commit log and on github itself.
\item[-] Was present at a vast majority (90\%+) of the coding, design, and presentation preparation meetings. On the two occasions I missed the coding meetings, I was very responsive and fixed encountered problems before the end of that day.
\item[-] Only missed a single day of class, and was never more than 2-3 minutes late, which happened once.
\item[-] Completed and updated an integral part of the application, visible through the site itself and the github history.
\end{itemize}

\end{document}